---
title: "A Sample Article Title"
short-title: "A Sample Running Head Title"
author:
  - name: Name1 Surname1
    email: first@somewhere.com
    orcid: 0000-0000-0000-0000
    note: "Some comment"
    affiliations:
      - name: University or Company Name
        department: Department
        city: City
        country: Country
  - name: Name2 Surname2
    email: second@somewhere.com
    affiliations:
      - name: Another University
        department: Department
        city: City
        country: Country
  - name: Name3 Surname3
    email: third@somewhere.com
    affiliations:
      - name: Third University
        department: Department
        city: City
        country: Country
abstract: |
  The abstract should summarize the contents of the paper. It should be clear, descriptive, self-explanatory and not longer than 200 words. It should also be suitable for publication in abstracting services. Formulas should be used as sparingly as possible within the abstract. The abstract should not make reference to results, bibliography or formulas in the body of the paper---it should be self-contained.
keywords: [first keyword, second keyword]
bibliography: references.bib
ims-journal: sts
# ims-journal: code passed to \documentclass[<code>]{imsart}.
# Numbered-citation journals (default; biblio-style: imsart-number):
#   sts  – Statistical Science
#   aos  – Annals of Statistics
#   aop  – Annals of Probability
#   aap  – Annals of Applied Probability
#   bj   – Bernoulli
#   aihp – Annales de l'Institut Henri Poincaré
#   ejs  – Electronic Journal of Statistics
#   ps   – Probability Surveys
#   ss   – Statistics Surveys
# Nameyear journals (set nameyear-cite: true and biblio-style: imsart-nameyear):
#   aoas – Annals of Applied Statistics
#   bjps – Brazilian Journal of Probability and Statistics
#   ba   – Bayesian Analysis
# nameyear-cite: true           # uncomment for nameyear journals (aoas, bjps, ba)
# biblio-style: imsart-nameyear # uncomment for nameyear journals
format:
  sts-pdf:
    keep-tex: true
header-includes: |
  \theoremstyle{plain}
  \newtheorem{axiom}{Axiom}
  \newtheorem{claim}[axiom]{Claim}
  \newtheorem{theorem}{Theorem}[section]
  \newtheorem{lemma}[theorem]{Lemma}
  \theoremstyle{definition}
  \newtheorem{definition}[theorem]{Definition}
  \newtheorem*{example}{Example}
  \newtheorem*{fact}{Fact}
---

# Introduction

This template helps you to create a properly formatted manuscript for IMS journals. Set the `journal` field in the YAML header to the appropriate journal code (e.g., `sts` for *Statistical Science*, `aos` for *Annals of Statistics*). Prepare your paper in the same style as used in this sample. Try to avoid excessive use of italics and bold face.

## Citation

For numbered citation journals, always use square brackets. For example, [@r1] or for multiple bibliography items [@r1; @r2; @r3; @r4]. For name-year citation journals, you can drop the square brackets for in-text citations.

# Fonts

Please use text fonts in text mode, e.g.:

-   Roman
-   *Italic*
-   **Bold**
-   [Small Caps]{.smallcaps}
-   `Typewriter`

Please use mathematical fonts in mathematical mode, e.g.:

-   $\mathrm{ABCabc123}$
-   $\mathit{ABCabc123}$
-   $\mathbf{ABCabc123}$
-   $\boldsymbol{ABCabc123\alpha\beta\gamma}$
-   $\mathcal{ABC}$
-   $\mathbb{ABC}$
-   $\mathsf{ABCabc123}$
-   $\mathtt{ABCabc123}$
-   $\mathfrak{ABCabc123}$

Note that `\mathcal` and `\mathbb` belong to capital letters-only font typefaces.

# Notes

Footnotes[^1] pose no problem.[^2]

[^1]: This is an example of a footnote.

[^2]: Note that footnote number is after punctuation.

# Environments

## Examples for Plain-Style Environments

Theorem environments are defined in `header-includes` and used as raw LaTeX blocks. This is required because the IMS class patches `\theoremstyle` in ways that are incompatible with Quarto's automatic theorem injection.

```{=latex}
\begin{axiom}\label{ax1}
This is the body of Axiom \ref{ax1}.
\end{axiom}

\begin{proof}
This is the body of the proof of the axiom above.
\end{proof}

\begin{claim}\label{cl1}
This is the body of Claim \ref{cl1}. Claim \ref{cl1} is numbered after Axiom \ref{ax1} because we used \verb|[axiom]| in \verb|\newtheorem|.
\end{claim}

\begin{theorem}\label{th1}
This is the body of Theorem \ref{th1}. Theorem \ref{th1} numbering is dependent on section because we used \verb|[section]| after \verb|\newtheorem|.
\end{theorem}

\begin{theorem}[Title of the theorem]\label{th2}
This is the body of Theorem \ref{th2}. Theorem \ref{th2} has additional title.
\end{theorem}

\begin{lemma}\label{le1}
This is the body of Lemma \ref{le1}. Lemma \ref{le1} is numbered after Theorem \ref{th2} because we used \verb|[theorem]| in \verb|\newtheorem|.
\end{lemma}

\begin{proof}[Proof of Lemma \ref{le1}]
This is the body of the proof of Lemma \ref{le1}.
\end{proof}
```

## Examples for Definition-Style Environments

```{=latex}
\begin{definition}\label{de1}
This is the body of Definition \ref{de1}. Definition \ref{de1} is numbered after Lemma \ref{le1} because we used \verb|[theorem]| in \verb|\newtheorem|.
\end{definition}

\begin{example}
This is the body of the example. Example is unnumbered because we used \verb|\newtheorem*| instead of \verb|\newtheorem|.
\end{example}

\begin{fact}
This is the body of the fact. Fact is unnumbered because we used \verb|\newtheorem*| instead of \verb|\newtheorem|.
\end{fact}
```

# Tables and Figures

Sample of cross-reference to figure. @fig-penG shows the estimated density of the standard normal distribution.

```{r}
#| label: fig-penG
#| fig-cap: "Kernel density estimate of 500 standard normal samples."
#| echo: false
library(ggplot2)
set.seed(42)
data.frame(x = rnorm(500)) |>
ggplot(aes(x = x)) +
  geom_density() +
  stat_function(fun = dnorm, linetype = 2) +
  labs(x = "x", y = "Density")
```

Cross-references to labeled tables: see @tbl-par.

```{r}
#| label: tbl-par
#| tbl-cap: "Linear model coefficient estimates (mtcars)"
#| echo: false
fit <- lm(mpg ~ wt + hp, data = mtcars)
coef_tbl <- broom::tidy(fit, conf.int = TRUE) |>
  dplyr::transmute(
    Parameter = term,
    Mean = estimate,
    `Std. dev` = std.error,
    `2.5%` = conf.low,
    `50%` = estimate,
    `97.5%` = conf.high
  )
knitr::kable(coef_tbl, digits = 3)
```

# Equations and the Like

Two equations:
$$
  C_{s}  =  K_{M} \frac{\mu/\mu_{x}}{1-\mu/\mu_{x}}
$$ {#eq-cs}
and
$$
  G = \frac{P_{\mathrm{opt}} - P_{\mathrm{ref}}}{P_{\mathrm{ref}}}  100(\%).
$$

Aligned equations:
\begin{align}
  \frac{dS}{dt} &= - \sigma X + s_{F} F,\\
  \frac{dX}{dt} &=   \mu    X,\\
  \frac{dP}{dt} &=   \pi    X - k_{h} P,\\
  \frac{dV}{dt} &=   F.
\end{align}

One long equation:
\begin{align*}
 \mu_{\text{normal}} &= \mu_{x} \frac{C_{s}}{K_{x}C_{x}+C_{s}}  \\
                     &= \mu_{\text{normal}} - Y_{x/s}\bigl(1-H(C_{s})\bigr)(m_{s}+\pi /Y_{p/s})\\
                     &= \mu_{\text{normal}}/Y_{x/s}+ H(C_{s}) (m_{s}+ \pi /Y_{p/s}).
\end{align*}

# Appendix {.appendix}

Appendices should be provided in the Appendix section, before Acknowledgements. If there is only one appendix, please refer to it as the Appendix. If there are multiple appendices, refer to them as Appendix A, Appendix B, etc.

::: {.acks}
The authors would like to thank the anonymous referees, an Associate Editor and the Editor for their constructive comments that improved the quality of this paper.
:::

::: {.funding}
The first author was supported by NSF Grant DMS-00-000000.

The second author was supported in part by NIH Grant 000000000.
:::

::: {.supplement stitle="Title of Supplement A" sdesc="Short description of Supplement A."}
:::

::: {.supplement stitle="Title of Supplement B" sdesc="Short description of Supplement B."}
:::
